### 2014-12-16 3-algorithms.tex
Merge detailed answers to reviewers comments

% input from observations.
Observation (\ref{havefeedAssum}) allows the crawler to obtain input for 
the extraction rule generation algorithm: each web feed entry contains a 
link to the corresponding web page as well as blog post article (either 
abstract or full text), its title, authors and publication date. We call 
these fields \emph{targets} as they constitute the data our crawler aims 
to extract. Observation (\ref{similarhtmlAssum}) guarantees the existence 
of an appropriate extraction rule, as well as its applicability to all 
posts of the blog.

@@

\begin{itemize}
\item\label{wordorderProp} Has low sensitivity to word ordering,
\item\label{lengthProp} Has low sensitivity to length variations,
\item\label{linearProp} Runs in linear time.
\end{itemize}

@@

With bigrams computed in this dynamic programming manner, the overall 
time to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} 
is linear. To conclude the proof that \autoref{linearAlgo} runs in linear 
time we show that all other computations of the inner loop can be done 
in constant \emph{amortized} time. As the number of edges in a tree is 
one less than the number of nodes, the \emph{amortized} number of bigrams 
unions per inner loop iteration tends to one. Each \emph{quotient of 
similarity} computation requires one bigrams intersection and three 
bigrams length computations. Over a finite alphabet (we used printable 
ASCII), bigrams sizes have bounded size and each of these operations 
takes constant time.

@@

Regarding time complexity, computing the \emph{tree distance} of each 
node of a graph to a single reference node can be done in linear time, 
and multiplying the number of targets by a constant factor does not 
affect the asymptotic computational complexity. Computing scores of 
comment extraction rules requires a more expensive algorithm. However, 
this is compensated by the fact that the proportion of candidates left, 
after filtering out rules not returning enough results, is very low in 
practice. Analogous reformulations to the one done with 
\autoref{linearAlgo} can be straightforwardly applied on each 
\code{ScoreFunction} to minimize the time spent in 
\coderef{similarityAlgo}.

>>>>

% input from observations.
Observation (\ref{havefeedAssum}) allows the crawler to obtain input for 
the extraction rule generation algorithm: each web feed entry contains a 
link to the corresponding web page as well as blog post article (either 
abstract or full text), its title, authors and publication date. We call 
these fields \emph{targets} as they constitute the data our crawler aims 
to extract. Observation (\ref{similarhtmlAssum}) guarantees the existence 
of an appropriate extraction rule, as well as its applicability to all 
posts of the blog. Each page is uniquely identified by its URL. If a page is already processed, it is not processed again in the future.

@@

\begin{enumerate}
\item\label{wordorderProp} Has low sensitivity to word ordering,
\item\label{lengthProp} Has low sensitivity to length variations,
\item\label{linearProp} Runs in linear time.
\end{enumerate}

@@

With bigrams computed in this dynamic programming manner, the overall 
time to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} 
is linear. To conclude the argument that \autoref{linearAlgo} runs in linear 
time we show that all other computations of the inner loop can be done 
in constant \emph{amortized} time. As the number of edges in a tree is 
one less than the number of nodes, the \emph{amortized} number of bigrams 
unions per inner loop iteration tends to one. Each \emph{quotient of 
similarity} computation requires one bigrams intersection and three 
bigrams length computations. Over a finite alphabet (we used printable 
ASCII), bigrams sizes have bounded size and each of these operations 
takes constant time.

@@

Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node and multiplying the number of targets by a constant factor can be done in linear time. However, computing scores of comment extraction rules requires a more expensive algorithm. This is compensated by the fact that the proportion of candidate HTML nodes left, after filtering out rules not returning enough results, is very low in practice. Analogous reformulations to the one done with \autoref{linearAlgo} can be straightforwardly applied on each ScoreFunction to minimize the time spent in \coderef{similarityAlgo} calculations.

It must be noted that there is no limitation due to comment nesting as long as comments follow the same format.

### 2014-12-16 5-evaluation.tex
Merge detailed answers to reviewers comments

>>>>

When compared to the other parts of crawling, the content extraction is sufficiently quick not to be a bottleneck. Indeed, extracting the content of 100 pages takes about half a second, downloading 100 pages takes at least 1 second, and, if enabled, rendering and taking screenshots takes about half a second per page.
